\newglossaryentry{must}
{	name={Must},
	description={This defines the first highest priority requirement.
	All of the tasks, requirements, or anything that is marked this way are
	build in the current version}
}

\newglossaryentry{should}
{	name={Should},
	description={This defines the second highest priority requirement. The system should implement 
	all of the tasks, requirements, or anything that is marked this way, but if 
	resources are limited, it can be left out of the current version.
	Build in next version}
}

\newglossaryentry{could}
{	name={Could},
	description={This defines the third highest priority requirement.The system could implement 
	all of the tasks, requirements, or anything that is marked this way, but if 
	resources are limited, it can be left out of the current and next version.
	Build in two versions from now}
}

\newglossaryentry{would}
{	name={Would},
	description={This defines the lowest priority requirement.  The system would like to implement 
all of the tasks, requirements, or anything that is marked this way, but only
if resources are available. It can be left out of all future versions}
}

\newglossaryentry{block}
{	name={Block},
	description={A piece that can be dragged in the drag and drop system of our uml project. Essentially, this referes to any individual object the user may drag and edit}
}

\newglossaryentry{diagram}
{	name={Diagram},
	description={A single individual result (essentially, a file) of our app. A diagram is essentially one single collection of blocks and whatever the user has added}
}